\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-08-06 Tex/PA_rrmemo/PA_RnR_memo.tex
add R2 to memo

\noindent \textbf{R2.1:} \emph{ }\\

>>>>

\noindent \textbf{R2.1:} \emph{ I would really like to see discussion near the end of section 4.1 potentially expanded and/or cleaned up considerably to make some things more clear.}\\

\noindent \textbf{R2.2:} \emph{ Additionally, implementation details are almost wholly relegated to the appendix; while this is largely appropriate, there is not even much information in the appendix, so I would recommend that one or both of the estimation details in the main paper and the appendix are expanded. What software was used? Do the authors generate novel convenience software to handle the specifics of the cERGM model and/or the computational overhead they discuss in the appendix?}\\

\noindent \textbf{R2.3:} \emph{ These issues that I mention are particularly important if the authors intend for this model to be used by the judicial politics community rather than only network modelers in other contexts where the cERGM structure makes sense; a bit more practical information would be necessary I think for this to travel within the judicial politics community.}\\

\noindent \textbf{R2.4:} \emph{ In many places the authors do a very good job of explaining the technical side of what they are doing precisely, as well as providing easy to digest intuitive explanations. However, one place where we seem to somewhat lack both clarity as well as thoroughness and precision is unfornately the section where it was arguably needed the most: the section on dependence terms. For example, the second paragraph of this section warns that "Unfortunately, adding the triangle, out-2-star, or in-2-star statistic causes model degeneracy," as far as I can tell, only for degeneracy as a result of the in-2-star statistic is a plan to guard against degeneracy addressed at all (surrounding equation (2)). I think more information about whether and how degeneracy resulting from the other statistics can be guarded against would be a good addition. Additionally, the authors fix the decay parameters for gwidegree and gwesp to 1 and 0.25 respectively with no discussion of the justification for those specific values; perhaps setting lambda for gwidegree to unity makes intuitive sense, but what drives the decision for gwesp? Considerably more guidance for applied researchers is needed in this section if the authors intend this model to be used by judicial politics researchers, which seems to be the case considering their discussion in the introduction. This would be a very good advance to the state of the art in citation studies in judicial politics, but the end of section 4.1 is not clear and thorough enough in my opinion to be useful to most applied judicial scholars whose work could be improved by the authors' methodological advance.}\\

\noindent \textbf{R2.5:} \emph{ As a small comment, in relation to the degeneracy discussion, I think footnote 4 would be best served by not being a footnote. After your discussion of degeneracy I think the typical reader will be wondering, "Did this end up being a problem for their application?" The answer is, "No, we checked that and it was fine," and I just think that as it's such a natural thing for a reader to want to know after you spent multiple full paragraphs discussing the issue, this sentence deserves its place in the main text.}\\

\noindent \textbf{R2.6:} \emph{ I think the manuscript would be greatly improved as well by pointing practitioners toward implementation software, even if this is a very short, simple statement. For example, if the answer for that is, "We used software X which is often used for ERGMs, and our custom calls to that software to handle the cERGM and large network we analyze can be found in the replication archive," great. If the authors have written convenience wrappers for existing software to handle these issues, or wholly novel software, even better; advertise it both for your own sake and for the sake of the substantive scholars who want to use your method because they care about modeling their data in the most appropriate way.}\\

\noindent \textbf{R2.7:} \emph{ I think the manuscript would be greatly improved as well by pointing practitioners toward implementation softwarA point which may be useful to the authors in future work (though I'm not sure whether they find it has great utility for this methods piece): The authors find that there are not reliable effects for the ideological variables, and thus wonder, "whether, and if so, how, citations are shaped by ideological factors." I think one natural response could be that the ideological effects may actually be found within the dependence effects they investigate in some way, and I wonder if there are creative ways within the context of their model to test for that.}\\
